Towards planning of infantile cardiac surgery based on simulation

### 2012-02-27 Doc/Miccai/shell-model.tex
miccai2012: few corrections
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@340 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b
miccai2012: images - convergence
git-svn-id: svn+ssh://scm.gforge.inria.fr/svnroot/sofa-shells@342 7b2761c9-2758-49ef-8c29-9c9f1e1aad1b

For more thorough description we refer the reader to the textbook about
Finite Elements for example \tomas{add ref}.

In the rest of the section we want to show that the performance of a model
based on the shell element is adequate for the simulation.

@@

The bending property of the shell allows us to use smaller number of
elements for the simulation and use high polygonal model only for
visualisation. The convergence of the model is a key factor here. In our experiments we
were able to use only as few as eight nodes around the circumference of a
tubular model while still maintaining realistic behaviour. Figure
\tomas{add-ref} shows the results for different number of nodes along the
circumference.

\tomas{image: convergence}

>>>>

For more thorough description we refer the reader to the textbook about
Finite Element methods for example \cite{Reddy1993}.

In the rest of the section we want to show that the performance of a model
based on shell elements is adequate for the simulation.

@@

The bending property of the shell allows us to use smaller number of
elements for the simulation and use high polygonal model only for
visualisation. The convergence of the model is a key factor here. In our
experiments we were able to use only as few as eight nodes around the
circumference of a tubular model while still maintaining realistic
behaviour. Figure \ref{fig-convergence} shows the results for different
number of nodes along the circumference.

\begin{figure}[tbh]
  \centering
  \begin{tabular}{cccc}
    \includegraphics[width=0.24\columnwidth]{img/twist-06-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-08-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-16-cg.png}
    &
    \includegraphics[width=0.24\columnwidth]{img/twist-31-cg.png}
  \end{tabular}
  \caption{Convergence on a twisted cylinder with 6, 8, 16 and 31 nodes
  around the circumference (120, 208, 832 and 3038 elements)}
  \label{fig-convergence}
\end{figure}
